THE HYDROGEN EPOCH OF REIONIZATION ARRAY DISH: CHARACTERIZATION OF THE INSTRUMENTAL RESPONSE WITH REFLECTOMETRY MEASUREMENTS AND ITS IMPLICATIONS ON THE MEASUREMENT OF 21CM POWER SPECTRUM.

### 2016-09-06 DishReflectometry/Paper1_v2.tex
Older changes, all of which are confusing

Since it was first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise and foregrounds four to five orders of magnitude
brighter than the signal ~\citep{2015ApJ...801..138P}, 
sky-averaged 21~cm monopole experiments such as
EDGES; ~\citep{Bowman_et_al2010},
BIGHORNS; ~\citealt{XXX},
SARAS; ~\citep{Patra_et_al2015} ,
SCIHI; ~\citep{2015PhDT........65V},
HYPERION; ~\citep{presley_et_al2015}
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

>>>>

Since first proposed in ~\citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
~\cite{furlanetto_et_al2006, morales_wyithe2010, pritchard_loeb2012}),
the technical path toward measuring this signal has been extremely challenging.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that are yet to be fully solved.  With noise temperatures dominated
by sky noise and foregrounds four to five orders of magnitude
brighter than the signal ~\citep{2015ApJ...801..138P}, 
sky-averaged 21~cm monopole experiments such as
EDGES; ~\citep{Bowman_et_al2010},
BIGHORNS; ~\citealt{XXX},
SARAS; ~\citep{Patra_et_al2015} ,
SCIHI; ~\citep{2015PhDT........65V},
HYPERION; ~\citep{presley_et_al2015}
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; ~\citealt{XXX}),
the Murchison Widefield Array (MWA; ~\citealt{XXX}),
the Giant Metre-wave Radio Telescope (GMRT; ~\citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; ~\citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; ~\citealt{XXX}),
and the future Square Kilometre Array (SKA; ~\citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.
